Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-11-27 supp/index.qmd
<edit struc>

---
title: "Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices"
author:
    - Robert Z. Selden, Jr.^[Heritage Research Center, Stephen F. Austin State University; Department of Biology, Stephen F. Austin State University; Texas Archeological Research Laboratory, The University of Texas at Austin; and Cultural Heritage Department, Jean Monnet University, zselden@sfasu.edu]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "Pilot study of elliptical biface morphology."
---

>>>>

---
title: "Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices"
author:
  - name: Robert Z. Selden, Jr.
    affiliations:
      - Heritage Research Center, Stephen F. Austin State University; Department of Biology, Stephen F. Austin State University; Texas Archeological Research Laboratory, The University of Texas at Austin; Cultural Heritage Department, Jean Monnet University
    email: zselden@sfasu.edu
    orcid: 0000-0002-1789-8449
  - name: John E. Dockall
    affiliations:
      - Stantec, Inc.
    email: john.dockall@stantec.com
    orcid: 0000-0002-0940-7144
  - name: David H. Dye
    affiliations: 
      - Department of Earth Sciences, The University of Memphis
    email: daviddye@memphis.edu
bibliography: [book.bib]
date: "`r format(Sys.time(), '%d %B, %Y')`"
link-citations: yes
github-repo: seldenlab/elliptical.bifaces
---
